\documentclass{resume}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Fan Cui}
\address{Phone: +44 7579 912812}
\address{Email: cuifaneo@gmail.com}

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University College London} \hfill {\em 09/2020 - 09/2021} \\ 
M.S. in Information Security \\

{\bf Zhejiang University} \hfill {\em 09/2016 - 07/2020} \\ 
B.S. in Computer Science \\
Overall GPA: 3.79/4 \\
Third year GPA: 3.99/4 Rank 5/122 \\
Mixed Class, Chu Kochen Honors College

\end{rSection}

%----------------------------------------------------------------------------------------
%	RESEARCH INTEREST SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Research Interest}

{\bf Machine Learning}\\ {\bf Distributed System}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Project and Research Experience}

\begin{rSubsection}{Department of Computer Science, Zhejiang University}{Hangzhou, China}{Dissertation Project}{12/2019 - 06/2020}
\item Design and implement {\bf an elevator fault forecasting model based on machine learning} (Cooperated with the Special Equipment Research Institute of Zhejiang Province).
\item The model is used to identify high-risk elevators with potential malfunction from all elevators in Zhejiang Province.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Pervasive Computing Lab, Zhejiang University}{Hangzhou, China}{Research Assistant}{07/2019 - 11/2019}
\item Re-implement {\bf the Spatiotemporal Multi-Graph Convolution Network (ST-MGCN)} for Ride-hailing Demand Forecasting.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Department of Computer Science, The University of Hong Kong}{Hong Kong, China}{Research Assistant}{07/2019 - 09/2019}
\item Assist Prof. Giulio Chiribella with the research of {\bf energy-preserving quantum channel}.
\item Prove two main theorems regarding energy-preserving quantum channel.
\item Retrofit {\bf the Grover's algorithm} to achieve $100\%$ accuracy with only $1/2$ energy consumption by introducing {\bf energy superposition}.
\item A paper in progress.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Advanced Computing and System Lab, Zhejiang University}{Hangzhou, China}{Research Assistant}{09/2017 - 04/2018}
\item Implement {\bf a prediction model for stock market trend} (Shanghai and Shenzhen 300 Index) using natural language processing and data mining.
\end{rSubsection}

\end{rSection}

\newpage

%----------------------------------------------------------------------------------------
%	SELECTED AWARDS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Selected Awards}

[10/2019] First-class Scholarship for Academic Excellence of Zhejiang University (ranked 5th of 122)
\newline
[12/2018] Third prize of College Physics Competition in Zhejiang Province
\newline
[10/2018] Third-class Scholarship for Academic Excellence of Zhejiang University
\newline
[10/2018] Outstanding Students of Zhejiang University
\newline
[10/2017] Third-class Scholarship for Academic Excellence of Zhejiang University

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & Mandarin(native), English(upper intermediate) \\
Programming Languages & C, C++, Python, C\#, Java, SQL, Matlab \\
Certificate (Coursera) & Certificate of Machine Learning by Stanford University \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	MISCELLANEOUS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Miscellaneous}

\begin{rSubsection}{St Antony's College, University of Oxford}{Oxford, England}{Exchange Student}{02/2019}
\item Series of seminars about cutting-edge research areas such as smart city, robotics, etc.
\end{rSubsection}

\begin{rSubsection}{Youth League, Zhejiang University}{Hangzhou, China}{Vice Minister}{09/2016 - 06/2018}
\item Organize college activities, such as Freshmen cocktail party, Welcome to ZJU labs.
\end{rSubsection}

%------------------------------------------------

\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
